\documentclass[a4paper,10pt]{article}

\usepackage[svgnames]{xcolor}
\usepackage[left=1.4cm,right=1.4cm,top=1.2cm,bottom=1.2cm]{geometry}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{ragged2e}
\usepackage{setspace}

\setmainfont{TeX Gyre Heros}
\setsansfont{TeX Gyre Heros}

\hypersetup{
  colorlinks=true,
  linkcolor=SteelBlue,
  urlcolor=SteelBlue,
  pdfauthor={Markus Schulte},
  pdftitle={Anti-CV: A Catalogue of Instructive Mistakes}
}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\footnotesize\textcolor{DimGray}{Page \thepage\ of 4 --- Still reading? You must enjoy other people's misfortune.}}

\titleformat{\section}{\large\bfseries\color{DarkSlateGray}}{}{0em}{}[\vspace{-0.5em}\textcolor{DarkOrange}{\rule{\linewidth}{1.2pt}}]
\titleformat{\subsection}{\normalsize\bfseries\color{SteelBlue}}{}{0em}{}
\titlespacing*{\section}{0pt}{0.7em}{0.3em}
\titlespacing*{\subsection}{0pt}{0.5em}{0.15em}

\setlist[itemize]{leftmargin=1.3em,itemsep=0.5pt,parsep=0.5pt,topsep=1pt}

\newcommand{\antimark}{\textcolor{DarkOrange}{\textbullet}}
\newcommand{\roleheader}[4]{%
  \subsection{#1}%
  \vspace{-0.2em}%
  {\small\textcolor{DimGray}{#2\enspace\textbar\enspace #3\enspace\textbar\enspace #4}}%
  \vspace{0.2em}%
}
\newcommand{\skullemoji}{\textcolor{DarkOrange}{\textsuperscript{$\dagger$}}}
\newcommand{\failbadge}[1]{{\scriptsize\colorbox{MistyRose}{\textcolor{Crimson}{\textbf{LESSON:}} \textcolor{DarkSlateGray}{#1}}}}

\begin{document}

% ============================================================
% PAGE 1
% ============================================================

\begin{center}
{\fontsize{26}{30}\selectfont\bfseries\textcolor{DarkSlateGray}{Markus Schulte}}\\[3pt]
{\large\textcolor{DarkOrange}{The Anti-CV}\enspace\textcolor{DimGray}{\textbar}\enspace
\textcolor{DimGray}{\textit{A Curated Collection of Failures, Questionable Decisions,}}}\\
\textcolor{DimGray}{\textit{and Lessons Learned the Hard Way Since 2007}}\\[5pt]
{\small
\textcolor{SteelBlue}{Freelance Cloud Architect \& Software Engineer}\enspace\textbar\enspace
Cologne, Germany\enspace\textbar\enspace
\href{mailto:mail@schulte-development.de}{mail@schulte-development.de}\enspace\textbar\enspace
+49\,178\,7217768}\\[1pt]
{\small
\href{https://schulte-development.de}{schulte-development.de}\enspace\textbar\enspace
\href{https://www.linkedin.com/in/markus-schulte/}{LinkedIn}\enspace\textbar\enspace
\href{https://github.com/SchulteDev}{GitHub}\enspace\textbar\enspace
\href{https://stackoverflow.com/users/1645517/markus-schulte}{StackOverflow (4000+ rep from answering things I previously got wrong)}}
\end{center}

\vspace{-0.2em}

\section{Executive Failure Summary}

\begin{spacing}{0.97}
{\small
\textbf{19+ years} in software engineering and cloud architecture. \textbf{12+ years freelance.}
On paper, that sounds impressive. In practice, it means 19+ years of picking the wrong technology,
underestimating deadlines, over-engineering solutions, and then writing retrospectives about how
much I learned. I have mass-produced microservices I later wished were monoliths, mass-produced
monoliths I later wished were microservices, and mass-produced JIRA tickets that made the previous
two sound intentional.

I once chose Sphinx over ElasticSearch because ElasticSearch felt ``too exotic.'' I accepted a
Head of Development role believing that being good at code meant being good at managing people
who write code. I built a crypto trading bot and am still not a millionaire. I spent 8 years
writing PHP before Java became my ``mother tongue'' --- take that, Stockholm syndrome. My
university degree took 8 years because I kept getting distracted by actual employment, which is
either commendable or a sign of poor planning, depending on your perspective.

On the bright side: platforms I have built serve 9M+ users, my production systems maintain 99.9\%
uptime, and I once saved a client 60 person-days with a single well-timed decision. So the
failures have been \textit{educational}.
}
\end{spacing}

\vspace{0.3em}

\section{Key Anti-Impacts: What Went Wrong (and Then Right)}

\vspace{-0.2em}

{\small
\begin{itemize}[leftmargin=1.5em]
\item[\antimark] \textbf{Chose Sphinx over ElasticSearch} because ES seemed ``exotic'' (2010).
The platform later migrated to ES anyway. I now do thorough evaluations (see: Algolia vs.\ ES,
which I actually got right in 2023).
\item[\antimark] \textbf{Promoted to Head of Dev at 23 with zero management experience.}
Assumed technical skill = leadership skill. Spent months focusing on UML diagrams while the team
needed a human being. Eventually trained myself into a laissez-faire leader. Team survived.
Barely.
\item[\antimark] \textbf{Spent 3 years building middleware that was architecturally unnecessary}
(Saloodo!). An AWS Lambda + eventing solution would have been cheaper, simpler, and faster.
The middleware did have 100\% uptime, though --- so at least the unnecessary thing worked perfectly.
\item[\antimark] \textbf{First microservices project at Trusted Shops (2018):} discovered that
``simple changes'' meant modifying 13+ repositories. Became a microservices skeptic. Now
advocate Self-contained Systems, which are microservices but with better marketing.
\item[\antimark] \textbf{Built a crypto-arbitrage trading bot} (2015). Technologies: Java,
machine learning, hope. Returns: educational. Net profit: let us talk about something else.
\item[\antimark] \textbf{Took 8 years for a 5-year degree} because I kept accepting paying
work. University calls it ``extended duration.'' I call it ``applied research with financial
compensation.''
\end{itemize}
}

\vspace{0.3em}

\section{Skills Overview (With Honesty Annotations)}

\vspace{-0.2em}

{\small
\begin{tabularx}{\textwidth}{>{\bfseries\color{DarkSlateGray}}l X}
Languages & Java (19y --- still surprised by generics edge cases), Golang (5y --- my happy place),
TypeScript/JS (functional when needed), PHP (8y --- we do not talk about PHP anymore) \\[3pt]
Cloud \& Infra & Azure (5y), AWS (7y), GCP (dabbled). Kubernetes (skeptic but proficient ---
it is a tool for platform teams, not for your TODO app). Docker, Terraform, Helm \\[3pt]
Architecture & Microservices (reformed), Self-contained Systems (convert), Event-driven (believer),
Monolith decomposition (therapist). R-methodology migration assessment \\[3pt]
Leadership & Teams of 5--9 devs, Product Owner (interim, reluctant), Agile Coach (Scrum, Kanban,
SAFe). Once fired a team member --- hardest correct decision I have made \\[3pt]
DevOps \& CI/CD & Jenkins (since 2010, before it was cool), Azure DevOps, GitHub Actions,
ArgoCD. Pipeline-as-Code evangelist. Reduced deployments from days to minutes \\[3pt]
Testing & JUnit, Mockito, Jest, Pact (contract testing workshop leader), Playwright, Selenium.
1000+ tests in 10-min builds. Testing: the thing I wish I had done more of, always \\[3pt]
Databases & PostgreSQL, MySQL, Oracle, MS-SQL, Redis. Optimized queries with EXPLAIN
(reduced SELECT times by 80\% at Saloodo! after discovering the existing ones were crimes) \\[3pt]
AI \& Search & Azure Document Intelligence, Algolia, ElasticSearch (we reconciled), Ollama/LLaMA,
Whisper.cpp --- currently building voice AI in Java because I enjoy punishment \\[3pt]
Soft Skills & Stakeholder translation (tech $\leftrightarrow$ business), writing documentation
nobody reads, presenting architecture decisions to committees that want bullet points
\end{tabularx}
}

\vfill

\newpage

% ============================================================
% PAGE 2
% ============================================================

\section{Recent Roles: Mistakes Made at Scale}

\roleheader{Cloud Architect --- LBBW (``Phoenix'' IT Modernization)}{Nov 2024 -- Oct 2025}{Freelance, Remote}{Germany's major state bank}

{\small
\textit{Tasked with migrating hundreds of legacy banking applications to Azure. The ``Skywalker''
platform. Yes, really. No, I did not name it.}
\begin{itemize}
\item Cataloged hundreds of legacy applications using R-methodology --- discovered that ``legacy''
is a polite word for ``nobody knows who built this or why it works.'' Each app needed
individualized migration; none came with documentation. Surprise.
\item Worked on a platform that was in development since 2023 but production-unused during my
engagement. My job: find the gaps. Found them. Many of them. Diplomatically.
\item Evaluated \href{https://elastisys.io/welkin/}{Elastisys Welkin} as a strategic alternative
--- because depending on a single platform is how you sleep well at night until you do not.
\item Created Solution Design Templates and applied them to FirstMover migrations. Sounds orderly.
In practice: teaching Spring Boot apps, Tomcat relics, and IIS survivors to coexist in Azure AKS
while meeting banking compliance. Each app thinks it is special. Each app is correct.
\item Ran Azure Calculator cost analyses. Discovered that cloud migration ``saving money'' requires
an asterisk the size of a footnote section.
\end{itemize}
\failbadge{Enterprise migration is 20\% technology, 80\% archaeology and diplomacy.}
}

\vspace{0.2em}

\roleheader{Software Lead \& Cloud Architect --- Union Investment}{Oct 2021 -- Dec 2024}{Freelance, Remote}{3+ year transformation, teams of 5--7}

{\small
\textit{Modernized InvestmentWelt (B2B sales platform, 80K users). ``Only'' 80K users, but each
one represented enough revenue to make downtime a career-ending event.}
\begin{itemize}
\item Designed Self-contained Systems architecture after analyzing a Liferay/FirstSpirit monolith
with 8 tangled domain boundaries. Drew many boxes and arrows. The boxes eventually became real
software. This still amazes me.
\item Built a custom microfrontend toolkit from scratch using Web Components. Chose to implement
directly after one PoC instead of exploring alternatives --- a ``bias for action'' that saved
\raise.17ex\hbox{$\scriptstyle\sim$}60 person-days. Or: got lucky and built a narrative around it.
\item Served as interim Product Owner and Agile Coach when the actual PO left. Learned that writing
user stories is harder than writing code. User stories do not have compilers to catch your errors.
\item Built the team from zero, onboarded members, established Kanban workflows. Also made the
difficult decision to remove a team member who was not working out. Nobody tells you that
leadership means having conversations you would rather not have.
\item Achieved 99.9\% uptime, 10-minute builds with 1000+ tests, deployment reduced from days to
30 minutes. The secret? Automation, paranoia, and a Renovate bot that never sleeps.
\item Designed cross-domain search using Azure Event Hubs $\rightarrow$ Algolia. The architecture
``initially seemed impossible'' --- then turned out to be a straightforward Pub/Sub pattern.
Lesson: the simplest solution is usually hiding behind your impostor syndrome.
\end{itemize}
\failbadge{Team composition matters more than architecture. People are not microservices --- you cannot just restart them.}
}

\vspace{0.2em}

\roleheader{Middleware Engineer --- Saloodo! (DHL Group)}{Dec 2021 -- Nov 2024}{Freelance, Part-Time, Remote}{Solo developer, Golang}

{\small
\textit{Took this part-time gig alongside Union Investment specifically to use Golang professionally.
Spent 3 years maintaining a system that, architecturally, should not have existed.}
\begin{itemize}
\item Sole engineer syncing \raise.17ex\hbox{$\scriptstyle\sim$}10M records between Saloodo and Salesforce. Solo ownership
means ``you build it, you run it, you get paged for it, you explain it.''
\item Achieved 100\% production uptime over 3 years. The system was architecturally unnecessary
(an AWS Lambda would have sufficed), but it was the most reliable unnecessary system I have ever built.
\item Optimized SQL queries by 80\% after discovering the existing schema contained malformed JSON,
incorrect types, and what I can only describe as ``creative data modeling.'' Built robust error
handling because the upstream data was a horror movie.
\item 70\% test coverage on 2,776 LOC with 5-second test runs using Dockertest.
Proof that quality standards pay for themselves even --- especially --- when you are alone.
\end{itemize}
\failbadge{Well-designed middleware cannot compensate for upstream chaos. Also: question whether the middleware should exist at all.}
}

\vspace{0.2em}

\roleheader{Senior Software Engineer --- Trusted Shops}{Aug 2018 -- Oct 2019}{Freelance, Cologne}{Subscription \& MARS teams}

{\small
\textit{My first encounter with a ``real'' microservices architecture. The disillusionment was swift.}
\begin{itemize}
\item Discovered that microservices meant modifying 13+ repositories for simple changes. Spent more
time on Terraform and pipeline YAML than on business logic. Became a lifelong microservices skeptic.
The architecture was not open to feedback. Neither was the YAML.
\item Built AWS Lambda templates with Micronaut, integrated Salesforce/Zuora/Twilio, refactored
services with Clean Code principles. Contributed to 13+ repos. Each repo had its own personality
and its own way of disappointing you.
\item Led Pact contract testing workshops --- trained 12 developers. Contract testing: the practice
of formally agreeing on APIs so you can formally blame someone when they break them.
\item Created reusable Lambda templates adopted team-wide. Finally, my over-engineering tendencies
produced something useful.
\end{itemize}
\failbadge{Microservices without automation and testing discipline are just a distributed monolith with network latency.}
}

\vfill

\newpage

% ============================================================
% PAGE 3
% ============================================================

\section{Earlier Roles: The Origin Story of My Skepticism}

\roleheader{Senior JavaEE Developer --- Allianz Global Digital Factory}{Nov 2017 -- Mar 2018}{Freelance via SinnerSchrader, Munich}{CloudFoundry, REST/HATEOAS}

{\small
\begin{itemize}
\item Deployed 3 applications to CloudFoundry (AWS-hosted). Created API documentation adopted as
company standard. Mentored 2 juniors in REST/HATEOAS --- a pattern whose name sounds like a
sneeze but whose principles are sound.
\item Short engagement, maximum acronym density: JavaEE, CF, AWS, REST, HATEOAS, SSO. Consultancy
bingo.
\end{itemize}
}

\vspace{0.15em}

\roleheader{Senior Engineer \& DevOp --- toom Baumarkt}{Oct 2016 -- Sep 2017}{Freelance via tarent solutions, Bonn}{``Butterkekse'' Scrum team (yes, named after cookies)}

{\small
\begin{itemize}
\item First encounter with Docker and Kubernetes. Kubernetes seemed overly complex then.
It still seems overly complex now. I have come to terms with it professionally while remaining
fundamentally skeptical personally. It is a tool for platform teams, not for your
three-endpoint service. I will die on this hill.
\item Accelerated E2E tests by 70\%, reduced JVM memory via GC tuning, introduced Swagger, OWASP,
and JMeter to the team. Led cross-team quality initiatives across 4 teams. Received formal
technical \textit{and} organizational recommendation letters --- apparently the cookie team liked me.
\item Wrote production services in Java, Golang, Ruby, and Shell. The polyglot experience taught me
that every language has its own way of making you feel inadequate.
\end{itemize}
\failbadge{Kubernetes: powerful, complex, and probably overkill for 90\% of what it is used for. But try saying that in a meeting.}
}

\vspace{0.15em}

\roleheader{PHP Developer $\rightarrow$ Head of Dev $\rightarrow$ Backend Dev --- werkenntwen}{Aug 2007 -- Jun 2014}{Permanent, Koblenz/Cologne}{Social network, 9M+ users, RIP 2014}

{\small
\begin{itemize}
\item Joined at 21 as a PHP developer. Promoted to Head of Development at 23. Nobody asked
``does he know how to manage people?'' The answer, it turned out, was ``not yet.'' Spent months
obsessing over UML diagrams while the team needed empathy and clear communication. Trained myself
into a laissez-faire leader through courses and painful self-reflection.
\item \textbf{The Sphinx Incident:} Chose Sphinx search over ElasticSearch because ES seemed
``exotic.'' The platform later migrated to ES anyway. This experience now fuels my obsessive
technology evaluations. Every thorough comparison I do today is an apology to 2010-me.
\item Scaled PHP architecture for 9M+ users with Memcache, table partitioning, and SQL-EXPLAIN
rituals. Reduced page load times by 60\%. Introduced Jenkins CI, PHPUnit, Selenium. Built REST APIs
with WADL documentation. Migrated entire systems to Zend Framework.
\item The company ceased operations on June 30, 2014. Sometimes your code is fine and the business
model is not. A humbling reminder that uptime means nothing if nobody is visiting.
\end{itemize}
\failbadge{Technical competence $\neq$ leadership competence. Also: bet on ``exotic'' technologies --- they are often just ``early.''}
}

\vspace{0.15em}

\subsection{Early Freelancing Highlights (2014--2016)}
{\small
\textcolor{DimGray}{\textit{The ``say yes to everything'' phase.}} Implemented CI/CD pipelines for
6+ companies (\textbf{YOOCHOOSE}, \textbf{Xsite}, \textbf{freshcells}, \textbf{fotocommunity},
\textbf{Silver Tours}/billiger-mietwagen.de, \textbf{AffiliCon}, \textbf{dailypresent}).
Jenkins consulting, Docker integration, PHP modernization, AWS migration, REST API development.
Reduced infrastructure costs by 40\% at one client. Learned that every company believes their
Jenkins setup is unique. None of them are.
}

\vspace{0.5em}

\section{Personal Projects: Where Ambition Meets Reality}

\vspace{-0.2em}

{\small
\begin{tabularx}{\textwidth}{>{\bfseries\color{DarkSlateGray}\raggedright}p{3.1cm} X}
ConversationalAI4J \newline\textcolor{DimGray}{\scriptsize 2025, Java 21} &
Voice-enabled conversational AI using local models. Spring Boot + Whisper.cpp + Piper TTS +
Ollama/LLaMA. Complete speech-to-text-to-LLM-to-speech pipeline in Java. Because when people
say ``Java is not for AI,'' I take it personally.
\href{https://github.com/SchulteDev/ConversationalAI4J}{\textcolor{SteelBlue}{GitHub}} \\[5pt]

SchulteDev Portfolio \newline\textcolor{DimGray}{\scriptsize 2025, Node.js} &
Monorepo for portfolio management with AI-powered CV generation using Claude, GitHub Actions
automation, and \LaTeX{} PDF generation. Yes, I automated my own CV. Yes, this document was
produced by that pipeline. Yes, I am aware of the irony of an Anti-CV generated by AI.
\href{https://github.com/SchulteDev/SchulteDev}{\textcolor{SteelBlue}{GitHub}} \\[5pt]

AI Tax Doc Processor \newline\textcolor{DimGray}{\scriptsize 2025, Golang} &
CLI tool using Azure Document Intelligence + SQLite for automated tax document capture.
I automated my tax paperwork because life is too short for manual data entry but apparently
not too short for building CLI tools.
\href{https://github.com/SchulteDev/Sse-BelMngr-Hermine}{\textcolor{SteelBlue}{GitHub}} \\[5pt]

Crypto Trading Bot \newline\textcolor{DimGray}{\scriptsize 2015, Java} &
Bitcoin arbitrage bot with machine learning (Weka, LibSVM). Technologies: Java, xChange API,
MySQL, hope, naivety. Financial outcome: I now have \textit{extensive knowledge} of cryptocurrency
market microstructure and exactly zero yachts. \\[5pt]

Bamboo Add-ons \newline\textcolor{DimGray}{\scriptsize 2016--2023, Java} &
Commercial Atlassian Marketplace plugins for code quality (Checkstyle, PMD, FindBugs).
83 customers in 15+ countries over 7 years. A sustainable business that quietly proved I could
ship product --- not just consulting hours.
\href{https://marketplace.atlassian.com/vendors/1213259}{\textcolor{SteelBlue}{Marketplace}}
\end{tabularx}
}

\vfill

\newpage

% ============================================================
% PAGE 4
% ============================================================

\section{Education: The Scenic Route}

{\small
\begin{tabularx}{\textwidth}{>{\bfseries\color{DarkSlateGray}\raggedright}p{3.2cm} X}
Diplom in Computer Science \newline\textcolor{DimGray}{\scriptsize 2004--2012} &
\textbf{University of Koblenz-Landau} --- Computational Visualistics \& Software Engineering.
Graduated with \textbf{distinction} (\textit{magna cum laude} equivalent). The German
\textit{Diplom} is equivalent to a Master of Science.\newline
\textbf{The catch:} It took 8 years instead of 5. I started working as a developer in 2007 and
kept getting distracted by the novelty of receiving actual money for writing code. The university
called it ``extended duration.'' My bank account called it ``solvency.'' In hindsight, the
parallel practical experience was genuinely valuable --- I just wish I had told the university
that on purpose. \\[6pt]

Abitur \newline\textcolor{DimGray}{\scriptsize 2003} &
Gymnasium Haren (Ems). Advanced courses: Mathematics \& Physics. Taught myself PHP in
2000--2003 using a PHP reference book. Built a forum for my friend group and later my graduating
class. This was the early 2000s; building a PHP forum was basically a rite of passage. My actual
IT education at school? A single typing course in 6th grade. Everything else was self-taught and
fueled by the desire to make websites and, if I am being honest, to play computer games ---
which directly led to choosing ``Computer Visualistics'' as my major.
\end{tabularx}
}

\vspace{0.3em}

\section{Certifications \& Community Standing}

{\small
\begin{tabularx}{\textwidth}{>{\bfseries\color{DarkSlateGray}\raggedright}p{3.2cm} X}
Java SE 8 TechCheck \newline\textcolor{DimGray}{\scriptsize IKM, June 2018} &
93/100, 88th percentile. Overall: ``Strong.'' 95\% proficient-or-strong across all subjects.
After 11 years of Java at that point, scoring 93 instead of 100 means 7\% of Java still
surprises me. Sounds about right. \\[4pt]
StackOverflow \newline\textcolor{DimGray}{\scriptsize Since 2012} &
4000+ reputation points. Mostly earned by answering questions about problems I had previously
struggled with myself. The circle of developer life. \\[4pt]
GitHub \newline\textcolor{DimGray}{\scriptsize Active} &
Open-source contributor. Public repos include ConversationalAI4J, portfolio tooling, and a
tax document processor. Proof that I write code voluntarily, which is either passion or a
concerning inability to stop.
\end{tabularx}
}

\vspace{0.3em}

\section{Additional Technical Opinions (Held Strongly, Updated Frequently)}

{\small
\begin{tabularx}{\textwidth}{>{\bfseries\color{DarkSlateGray}\raggedright}p{3.2cm} X}
On Kubernetes & A tool for platform engineering teams. Not for your three-container app. I have
used it extensively at toom, Saloodo!, Trusted Shops, and LBBW. I remain skeptical it is the
right default. Hyperscalers offer simpler options. I will use K8s when it is warranted and
complain about it regardless. \\[4pt]
On Microservices & Was a true believer until Trusted Shops (2018), where simple changes meant
13+ repo modifications. Now advocate Self-contained Systems: enough autonomy to be useful,
enough cohesion to be maintainable. SCS at Union Investment validated this approach. \\[4pt]
On ``Best Practices'' & Best practices are ``things that worked somewhere else.'' I apply them
rigorously (SCS, contract testing, IaC, CI/CD, test pyramids) but always verify they fit the
context. The most expensive architecture is one copied from a blog post without understanding why. \\[4pt]
On Quality & Every project where I invested in testing and automation paid dividends in velocity.
Every project where I did not, I regretted it. This pattern has held for 19 years. I am a slow
learner, but I am consistent.
\end{tabularx}
}

\vspace{0.3em}

\section{Career Breaks: Intentional and Otherwise}

{\small
\begin{tabularx}{\textwidth}{>{\bfseries\color{DarkSlateGray}\raggedright}p{3.2cm} X}
Parental Leave \newline\textcolor{DimGray}{\scriptsize Apr 2020 -- Sep 2021} &
18 months during COVID-19. Combined family time with an industry-wide project freeze.
Discovered that debugging a toddler is harder than debugging distributed systems:
no stack traces, no logs, unpredictable behavior, and the error messages are just screaming. \\[4pt]
Travel Break \newline\textcolor{DimGray}{\scriptsize Aug -- Dec 2015} &
Explored different countries and cultures. Returned with perspective, a questionable tan, and the
conviction that building a crypto trading bot was a good idea. (See: Personal Projects.) \\[4pt]
Military Service \newline\textcolor{DimGray}{\scriptsize Aug 2003 -- Mar 2004} &
Mandatory service. Air force, basic training at Nassau-Dietz-Barracks (Budel, NL), then Hopsten
airbase (Rheine, DE). Learned discipline, early mornings, and that I preferred compilers to
commanding officers. The first and last time someone else determined my deployment schedule.
\end{tabularx}
}

\vspace{0.3em}

\section{The Honest Summary}

{\small
19 years in, and the most important lesson is the simplest: \textit{you learn more from what
goes wrong than from what goes right.} I chose the wrong search engine, built unnecessary
middleware, underestimated leadership, over-complicated architectures, and took 8 years to
finish a 5-year degree. But each failure refined my judgment. Today, I evaluate technologies
obsessively (because of Sphinx), question architectural complexity (because of microservices),
invest in testing religiously (because of Saloodo!), and lead with empathy first (because of
werkenntwen). The failures are the features.

\textbf{My actual slogan:} ``Crafting solutions that thrive today and tomorrow'' ---
after extensive post-mortems of the ones that did not.
}

\vfill

\begin{center}
\textcolor{DimGray}{\rule{0.8\linewidth}{0.4pt}}\\[4pt]
{\scriptsize\textcolor{DimGray}{
\textbf{AI Transparency Disclaimer:} This document was generated with AI assistance
(Anthropic Claude) from comprehensive, human-authored career data. All experiences,
failures, lessons, and self-deprecating remarks are factually grounded in real professional
history. The humor was collaboratively developed; the mistakes were entirely my own.
Last compiled: \today.}}
\end{center}

\end{document}