\documentclass[11pt,a4paper]{article}
\usepackage{geometry}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{fancyhdr}

\geometry{top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm}
\setmainfont{Latin Modern Roman}
\setsansfont{Latin Modern Sans}
\setmonofont{Latin Modern Mono}

\definecolor{darkblue}{RGB}{0,47,108}
\definecolor{lightgray}{RGB}{220,220,220}

\titleformat{\section}{\Large\bfseries\sffamily\color{darkblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries\sffamily}{}{0em}{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.3em}
\pagestyle{empty}

\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue,
    pdfauthor={Markus Schulte},
    pdftitle={Markus Schulte - Cloud Architect CV}
}

\begin{document}

% Page 1
{\LARGE\bfseries\sffamily Markus Schulte}\\[0.2em]
{\large\sffamily Cloud Architect \& Software Engineer}\\[0.5em]
\href{mailto:mail@schulte-development.de}{mail@schulte-development.de} $\bullet$ 
\href{tel:+4917872177768}{+49 178 7217768} $\bullet$
\href{https://schulte-development.de}{schulte-development.de}\\
\href{https://www.linkedin.com/in/markus-schulte/}{linkedin.com/in/markus-schulte} $\bullet$
\href{https://github.com/SchulteDev}{github.com/SchulteDev}\\[0.5em]

\section*{Professional Summary}

Cloud Architect with 18+ years experience (11+ freelance) specializing in enterprise cloud transformations. Currently leading LBBW's Phoenix modernization, architecting Azure migration for Germany's major state bank. Expert in cloud-native design, microservices, and DevOps with proven track record of delivering platforms serving 9M+ users.

\section*{Key Business Impact}

\begin{itemize}[leftmargin=0.5cm,itemsep=0.2em]
\item \textbf{Enterprise Scale:} Led cloud transformations for major financial institutions (LBBW, Union Investment)
\item \textbf{Platform Performance:} Reduced deployment times from days to 30 minutes, achieved 99.9\% uptime
\item \textbf{Team Leadership:} Managed teams of 5-9 developers, served as Product Owner and technical mentor
\item \textbf{Architecture Excellence:} Established patterns adopted as corporate standards across organizations
\item \textbf{Revenue Generation:} Built sustainable 7-year product business with 83 global customers
\end{itemize}

\section*{Technical Expertise}

\begin{tabularx}{\textwidth}{X X}
\textbf{Cloud Platforms} & \textbf{Programming Languages} \\
AWS (7+ years): EKS, Lambda, S3, CloudFormation & Java (18+ years): Spring Boot, Quarkus, Micronaut \\
Azure (4+ years): AKS, Functions, Static Web Apps & Golang (4+ years): Microservices, Event Processing \\
GCP, Kubernetes, Docker, Terraform & TypeScript/JavaScript, PHP (8+ years) \\[0.5em]

\textbf{Architecture Patterns} & \textbf{DevOps \& Quality} \\
Microservices, Event-Driven Architecture & CI/CD: Jenkins, Azure DevOps, GitHub Actions \\
Self-contained Systems (SCS), API Design & Testing: Unit, Integration, Contract (Pact), E2E \\
Legacy Modernization, Multi-Cloud Strategies & Monitoring: ELK, Grafana, Application Insights \\
\end{tabularx}

\section*{Current Engagement}

\subsection*{Cloud Architect at LBBW | Nov 2024 – Present | Remote}

Leading \textbf{Phoenix IT modernization} for major German state bank. IT-architectural responsibility for 10 of 30 applications in Azure migration initiative. Working in 80-person transformation program as technical cloud architect for ``04 – Application Development'' area.

\textbf{Key Contributions:}
\begin{itemize}[leftmargin=0.5cm,itemsep=0.1em]
\item Architecting FirstMover migrations to Azure with Solution Design Template definition
\item Developing multi-cloud strategy (Azure, Elastisys Welkin) for enterprise flexibility
\item Conducting technical assessments across Spring Boot, Tomcat, IIS application portfolio
\item Leading architecture workshops and presenting solutions to business/IT committees
\end{itemize}

% Page 2
\newpage
\section*{Selected Professional Experience}

\subsection*{Cloud Architect at Union Investment | Oct 2021 – Dec 2024 | Remote}

Led 3+ year transformation of business-critical B2B sales platform InvestmentWelt serving 80,000 users. Managed teams of 5-7 developers as technical Product Owner.

\textbf{Architecture \& Leadership:}
\begin{itemize}[leftmargin=0.5cm,itemsep=0.1em]
\item Transformed monolithic Liferay platform into distributed Self-contained Systems architecture
\item Designed event-driven architecture across 8 business domains using Azure Event Hubs
\item Led development of microfrontend-toolkit framework adopted as corporate standard
\item Served as Product Owner defining sprint goals and managing agile development
\end{itemize}

\textbf{Technical Excellence:}
\begin{itemize}[leftmargin=0.5cm,itemsep=0.1em]
\item Built comprehensive CI/CD pipeline with Infrastructure-as-Code using Terraform
\item Achieved 10-minute build cycles despite 1000+ tests through parallelization
\item Implemented unified search across distributed systems using Algolia
\item Reduced deployment time from days to 30 minutes, achieved 99.9\% uptime
\end{itemize}

\textbf{Business Impact:} Established architecture patterns adopted group-wide, enabled 10x faster deployments, sub-second search response times across all domains.

\subsection*{Middleware Engineer at Saloodo! (DHL Group) | Dec 2021 – Nov 2024 | Part-time Remote}

Sole developer for critical middleware synchronizing ~10 million records between Saloodo platform and Salesforce CRM.

\textbf{Technical Achievements:}
\begin{itemize}[leftmargin=0.5cm,itemsep=0.1em]
\item Designed fault-tolerant Golang service with 100\% production uptime over 3 years
\item Implemented multi-threaded bulk processing for 10M+ record synchronization
\item Achieved 70\% test coverage with 5-second test execution using Dockertest
\item Built comprehensive monitoring with ELK Stack and Dynatrace
\end{itemize}

\subsection*{Cloud Consultant at Trusted Shops | Aug 2018 – Oct 2019 | Cologne}

Modernized e-commerce trust provider's legacy JavaEE6 systems to cloud-native architecture on AWS.

\textbf{Key Deliverables:}
\begin{itemize}[leftmargin=0.5cm,itemsep=0.1em]
\item Designed serverless solutions using AWS Lambda, API Gateway, and S3
\item Led contract testing implementation with Pact framework across teams
\item Integrated Salesforce, Zuora, and Twilio for subscription management
\item Created reusable AWS Lambda templates with Micronaut framework
\end{itemize}

\textbf{Impact:} Successfully migrated legacy systems reducing maintenance overhead, established cloud-native CI/CD pipelines, trained teams in modern testing practices.

% Page 3
\newpage
\section*{Earlier Professional Experience}

\subsection*{Senior Engineer \& DevOp at toom Baumarkt | Oct 2016 – Sep 2017 | Bonn}
Led ``Butterkekse'' development team (8 members) with cross-team quality leadership. Delivered 5 production microservices using Java and Golang. Reduced deployment time from days to hours, achieved 70\% test execution improvement. Introduced Swagger, Docker containerization, and comprehensive metrics.

\subsection*{Creator of Atlassian Bamboo Add-ons | Jun 2016 – Dec 2023 | Self-Employed}
Built sustainable product business with 83 customers across 15+ countries. Developed Java-based add-ons for code quality integration (Checkstyle, PMD, FindBugs). Generated recurring revenue over 7 years with global enterprise adoption.

\subsection*{Senior JavaEE Developer at Allianz Global Digital Factory | Nov 2017 – Mar 2018 | Munich}
Deployed 3 applications to CloudFoundry (AWS) for Allianz digital initiatives. Implemented REST/HATEOAS APIs with comprehensive documentation adopted as company standard.

\subsection*{Early Freelance Projects | Jan 2014 – Aug 2016}
\begin{itemize}[leftmargin=0.5cm,itemsep=0.1em]
\item \textbf{YOOCHOOSE:} Spring applications, Jenkins CI, AWS operations
\item \textbf{Xsite:} REST API development, Jenkins pipeline-as-code
\item \textbf{freshcells:} Docker CI implementation, PHP quality standards
\item \textbf{Silver Tours:} Infrastructure modernization for car rental platform
\end{itemize}

\subsection*{PHP Developer \& Head of Development at werkenntwen | Aug 2007 – Jun 2014 | Permanent}
Scaled architecture for 9M+ registered users on Germany's major social network. Led transformation from procedural to object-oriented architecture. Managed development team with full personnel responsibility. Achieved 60\% page load improvement through modernization.

\section*{Personal Projects}

\subsection*{SchulteDev Portfolio Repository | 2025}
AI-powered CV generation using Claude 4 with GitHub Actions automation. LaTeX document generation with automated releases. \href{https://github.com/SchulteDev/SchulteDev}{github.com/SchulteDev/SchulteDev}

\subsection*{AI Document Processing for Tax Software | Jan – May 2025}
CLI application using Azure Document Intelligence for automated document capture. Integration with SteuerSparErklärung tax software. Built with Golang and SQLite.

\subsection*{Jenkins-GitHub Integration PoC | Apr – Jul 2018}
Multi-tenant architecture enabling automatic Jenkins setup for GitHub repositories. Technologies: Google Cloud, Firebase, Java, TypeScript, Golang.

% Page 4
\newpage
\section*{Education}

\subsection*{Diploma in Computer Science | University of Koblenz-Landau | 2004 – 2012}
\textbf{Degree:} Diploma (equivalent to Master of Science)\\
\textbf{Grade:} Distinction (magna cum laude equivalent)\\
\textbf{Focus:} Computational Visualistics and Software Engineering\\
\textbf{Note:} Extended duration due to parallel professional work starting 2007

\subsection*{Abitur | Gymnasium Haren | 2003}
Advanced courses in Mathematics and Physics

\section*{Skills Summary}

\textbf{Leadership \& Business:} Team management (5-9 developers), Product Owner experience, stakeholder communication, architecture governance, agile coaching, technical mentoring

\textbf{Cloud \& Infrastructure:} AWS (7+ years), Azure (4+ years), Kubernetes, Docker, Terraform, Infrastructure-as-Code, serverless architectures, multi-cloud strategies

\textbf{Development:} Java (18+ years), Golang (4+ years), TypeScript/JavaScript, PHP, microservices, event-driven architecture, API design, legacy modernization

\textbf{Quality \& DevOps:} CI/CD pipelines, contract testing (Pact), comprehensive test automation, monitoring (ELK, Grafana), SonarQube, build optimization

\textbf{Languages:} German (native), English (fluent)

\section*{Career Breaks}

\textbf{Parental Leave:} Apr 2020 – Sep 2021 (COVID-19 pandemic)\\
\textbf{Personal Travel:} Aug – Dec 2015\\
\textbf{Military Service:} Aug 2003 – Mar 2004 (mandatory)

\section*{Certifications \& Recognition}

\begin{itemize}[leftmargin=0.5cm,itemsep=0.1em]
\item Java SE 8 TechCheck: 93/100 score, 88th percentile (2018)
\item StackOverflow: 4000+ reputation points
\item Multiple professional recommendations from tarent, AffiliCon, dailypresent
\end{itemize}

\vfill
\begin{center}
\footnotesize\textit{This CV was generated using AI assistance (Claude 4) from comprehensive career documentation.\\
The content accurately represents my professional experience and achievements.}
\end{center}

\end{document}