\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2cm]{geometry}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{array}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{wasysym}
\definecolor{darkblue}{RGB}{0,0,139}
\definecolor{darkred}{RGB}{139,0,0}
\definecolor{darkgreen}{RGB}{0,100,0}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue,
    citecolor=darkblue
}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.4pt}
\lfoot{The Anti-CV of Markus Schulte}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\begin{document}
\begin{center}
{\LARGE \textbf{MARKUS SCHULTE}}\\[8pt]
{\large \textit{The Unvarnished Truth About a Cloud Architect}}\\[6pt]
{\small \texttt{mail@schulte-development.de} $\bullet$ +49 178 7217768 $\bullet$ Cologne, Germany}\\
{\small \href{https://schulte-development.de}{schulte-development.de} $\bullet$ \href{https://github.com/SchulteMarkus}{GitHub} $\bullet$ \href{https://www.linkedin.com/in/markus-schulte/}{LinkedIn}}
\end{center}
\vspace{12pt}
\section*{Executive Summary of Professional Inadequacies}
\textbf{Warning:} This document contains unfiltered truths about 18+ years of stumbling through software engineering, including 11+ years of convincing clients I know what I'm doing as a freelancer.
\textbf{Current Status:} Pretending to be a Cloud Architect at LBBW since November 2024, where I've already discovered that 50\% of their applications are incompatible with their shiny new platform. Previous victims include Union Investment (3 years of over-engineering), DHL's Saloodo! (solo midnight debugging sessions), and various other companies who mistook my confidence for competence.
\textbf{Core Delusions:} I claim expertise in Java (my ``mother tongue'' -- as if code languages need maternal metaphors), Golang (because Java wasn't hipster enough), and cloud platforms (AWS, Azure, GCP -- collecting them like Pokemon cards). I've ``architected'' everything from microservices to monolith migrations, usually making things more complex than necessary.
\textbf{Notable Failures:} Successfully turned simple problems into distributed systems nightmares. Introduced ``Self-contained Systems'' at Union Investment -- a fancy term for ``we couldn't agree on one architecture.'' Built a Golang middleware at Saloodo! that handles 10 million records because apparently, I enjoy suffering. Created Atlassian add-ons that 83 companies now depend on -- their mistake, not mine.
\textbf{Leadership Disasters:} Managed teams of 5-9 developers who somehow still talk to me. Served as interim Product Owner, proving that engineers shouldn't make business decisions. Conducted ``architecture workshops'' where I confidently explained patterns I'd only read about the night before.
\textbf{Academic Pretensions:} Diplom in Computer Science from University of Koblenz-Landau (2004-2012), where I spent 8 years learning things I'd immediately forget. Focused on ``Computer Visualistics'' -- yes, that's a real thing, and no, I can't explain it either.
\textbf{Personal Confessions:} Took a convenient ``parental leave'' during COVID (April 2020 - September 2021) when the job market looked scary. Currently building an AI tax helper because even I don't understand German tax law. Once built a crypto trading bot (2015) that probably lost money -- thankfully, I'll never know.
\textbf{Fair Warning:} Despite this brutal honesty, companies keep hiring me. Either they appreciate transparency, or the IT industry is more desperate than we thought. Proceed with caution.
\newpage
\section*{The Comprehensive Catalog of Professional Missteps}
\subsection*{Why You Shouldn't Hire Me (But Probably Will Anyway)}
Let me save you time by listing all the reasons this CV should go straight to the rejection pile:
\begin{itemize}[leftmargin=*]
\item \textbf{Chronic Over-Engineering:} Give me a simple CRUD app, and I'll return a distributed system with 17 microservices, 3 message queues, and a 47-page architecture document
\item \textbf{Buzzword Addiction:} I've never met a technology I didn't want to try. My GitHub is a graveyard of half-finished experiments
\item \textbf{Meeting Terrorist:} I ask uncomfortable questions like ``What problem are we actually solving?'' and ``Have we considered not using blockchain?''
\item \textbf{Documentation Extremist:} I write README files longer than the actual code. Yes, I'm that person
\item \textbf{Test Coverage Zealot:} I once spent 3 days writing tests for a 50-line function. The tests had bugs
\end{itemize}
\subsection*{Career Lowlights (2007-2024)}
\subsubsection*{Current Disaster: LBBW (Nov 2024 - Present)}
\textit{Cloud Architect / Professional Bad News Bearer}
Currently destroying hopes and dreams at Germany's state bank by informing them that their ``Phoenix'' modernization project is more like a dodo. Highlights of my destruction:
\begin{itemize}[leftmargin=*]
\item Cataloged hundreds of legacy applications, discovering most are held together by prayers and PHP 5.3
\item Identified that 50\% of applications are incompatible with their new platform (Skywalker) -- yes, they named it after Star Wars
\item Creating ``migration strategies'' which is consultant-speak for ``this is going to hurt''
\item Writing cost analyses that make executives cry into their Azure Calculators
\item Participating in meetings where I explain why ``just moving it to the cloud'' isn't a strategy
\end{itemize}
\textbf{Technologies Abused:} Azure (when it works), Kubernetes (when I remember the commands), Oracle (unfortunately), MS-SQL (also unfortunately), draw.io (for diagrams no one reads)
\subsubsection*{Union Investment's Frankenstein Project (Oct 2021 - Dec 2024)}
\textit{Cloud Architect / Over-Engineering Specialist}
Spent 3 years turning a simple website into a distributed systems masterpiece that no one asked for:
\begin{itemize}[leftmargin=*]
\item Transformed a working monolith into 8 ``Self-contained Systems'' because I read a Medium article about it
\item Convinced them to use Web Components, a standard so cutting-edge that browser support is still questionable
\item Built a ``microfrontend-toolkit'' -- yes, I created a framework to solve problems I created
\item Implemented event-driven architecture for a search feature that could have been a simple database query
\item Achieved 10-minute build times for 1000+ tests, spending more time optimizing builds than writing features
\item Introduced 47 different npm packages because apparently, we needed a library for left-padding strings
\end{itemize}
\textbf{Damage Assessment:} 
\begin{itemize}[leftmargin=*]
\item Deployment time reduced from days to 30 minutes (it was 5 minutes before I ``improved'' it)
\item Created job security for 3 DevOps engineers just to maintain my complexity
\item Search now requires 5 Azure services to find 80,000 users
\end{itemize}
\subsubsection*{Saloodo!'s Midnight Debugging Adventures (Dec 2021 - Nov 2024)}
\textit{Middleware Engineer / Solo Masochist}
Accepted a part-time role because ``how hard could syncing data be?'' Narrator: It was very hard.
\begin{itemize}[leftmargin=*]
\item Single-handedly maintained a Golang service processing 10 million records
\item Discovered Saloodo's database had ``creative'' interpretations of data types
\item Implemented ``robust error handling'' (aka try-catch everything and pray)
\item Achieved 100\% uptime by never deploying on Fridays
\item Wrote 70\% test coverage, the other 30\% is covered by hope
\item Experienced the joy of being on-call for a system only I understood
\end{itemize}
\textbf{Personal Growth:} Learned that ``it works on my machine'' doesn't count when you're the only machine
\subsubsection*{The Atlassian Add-on Empire (2016 - 2023)}
\textit{Accidental Entrepreneur / Bug Provider}
Created Bamboo add-ons because Atlassian's ecosystem wasn't complex enough:
\begin{itemize}[leftmargin=*]
\item Built add-ons for Checkstyle, PMD, FindBugs -- tools that find bugs in code (ironic, I know)
\item Convinced 83 companies worldwide to depend on software maintained by one person
\item Provided ``24/7 support'' (I checked emails before bed)
\item Earned the title ``Marketplace Partner'' which sounds impressive but means ``we take 25\% of your revenue''
\item Sunset the products when Atlassian decided Server products were so 2022
\end{itemize}
\subsubsection*{The Freelance Years of Confusion (2014 - 2020)}
A greatest hits collection of short-term contracts where I:
\begin{itemize}[leftmargin=*]
\item \textbf{Trusted Shops:} Migrated from JavaEE6 (vintage 2009) to ``cloud-native'' (aka more expensive)
\item \textbf{TOOM Baumarkt:} Introduced microservices to a hardware store's IT. They needed 2 services. I built 7
\item \textbf{Allianz:} Wrote REST APIs so RESTful they put developers to sleep
\item \textbf{Sedo:} Consolidated services then immediately suggested splitting them again
\item \textbf{Various Others:} Left a trail of Jenkins pipelines and confused developers across Germany
\end{itemize}
\subsubsection*{The PHP Years I Try to Forget (2007 - 2014)}
\textit{wer-kennt-wen.de / Head of Development}
Started as a PHP developer, somehow became Head of Development. Clear proof that companies make questionable decisions:
\begin{itemize}[leftmargin=*]
\item Led a team of 8 developers who knew more than me
\item Scaled a social network to 500K users using technology held together by duct tape
\item Introduced ``Agile methodologies'' (we had daily standups where everyone stood)
\item Migrated from ``legacy PHP'' to ``modern PHP'' (added more semicolons)
\item Left when Facebook killed local social networks (great timing on my part)
\end{itemize}
\subsection*{Skills I Claim to Have}
\subsubsection*{Programming Languages (Order of Delusion)}
\begin{itemize}[leftmargin=*]
\item \textbf{Java (18+ years):} I call it my ``mother tongue'' but I still Google ``how to sort ArrayList''
\item \textbf{Golang (4+ years):} Adopted it because ``Java is too verbose'' then wrote verbose Go
\item \textbf{PHP (8+ years):} The language that started it all. I'm sorry
\item \textbf{JavaScript/TypeScript:} I know enough to be dangerous, especially with \texttt{npm install}
\end{itemize}
\subsubsection*{Cloud Platforms (All Equally Confusing)}
\begin{itemize}[leftmargin=*]
\item \textbf{AWS:} I can spell EC2, S3, and accidentally create \$10,000 monthly bills
\item \textbf{Azure:} Microsoft's cloud. Like AWS but with different names for everything
\item \textbf{GCP:} Google's cloud. I used it once. It was cloudy
\end{itemize}
\subsubsection*{Architectural Patterns I've Misapplied}
\begin{itemize}[leftmargin=*]
\item Microservices (when 3 services would do, I build 30)
\item Event-Driven Architecture (everything is an event, even login)
\item Self-contained Systems (containers containing containers containing confusion)
\item Monoliths (I can build these too, just give me time)
\end{itemize}
\subsection*{Education: 8 Years for a 4-Year Degree}
\textbf{University of Koblenz-Landau (2004-2012)}\\
Diplom in Computer Science (it's like a Master's but sounds fancier)
\begin{itemize}[leftmargin=*]
\item Focused on ``Computer Visualistics'' -- even my professors couldn't explain it
\item Thesis on something I've completely forgotten but got good marks
\item Learned algorithms I've never used since
\item Expert at extending student life to avoid real work
\end{itemize}
\subsection*{Personal Projects (Procrastination Disguised as Learning)}
\subsubsection*{AI Tax Helper (2025)}
Built an AI to do my taxes because:
\begin{itemize}[leftmargin=*]
\item German tax law is scarier than production deployments
\item I needed an excuse to use Azure Document Intelligence
\item The alternative was actually learning tax law
\end{itemize}
\subsubsection*{Crypto Trading Bot (2015)}
\begin{itemize}[leftmargin=*]
\item Built during the ``blockchain will solve everything'' era
\item Used machine learning (aka random number generation with extra steps)
\item Results: Classified. Probably for the best
\end{itemize}
\subsection*{Life Choices Masquerading as Career Decisions}
\begin{itemize}[leftmargin=*]
\item \textbf{Military Service (2003-2004):} Learned that following orders is easier than thinking
\item \textbf{Career Break (2015):} ``Transitioning to freelance'' (aka unemployed with ambition)
\item \textbf{Parental Leave (2020-2021):} Perfectly timed with a global pandemic. Strategic genius or lucky accident?
\end{itemize}
\subsection*{References}
Available upon request, though I haven't asked them if they'd recommend me. Surprise references are more fun.
\subsection*{Final Disclaimer}
Despite everything you've read, I somehow continue to get hired and deliver projects. This either speaks to my hidden competence or the IT industry's desperation. You decide.
\textit{``The best code is no code, but I'll write 10,000 lines to prove it.''} -- Me, probably
\end{document}